---
title: "MyShinyApp Presentation"
author: "Laurel Mayhew"
date: "June 19, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## The data

MyShinyApp is a shiny application that displays data from US Named Hurricanes.
The Names US Atlantic Hurricanes data is from the R package "DAAG" 
and gives details of atmosperic pressure and windspeed at landfall,
estimated damage in millions of dollars and deaths for named
hurricanes that made landfall in the US mainland from 1950 to 2012.

The GitHub url is 
[https://github.com/LMayhew/MyShinyApp](https://github.com/LMayhew/MyShinyApp).

MyShinyApp is located at
[https://lmayhew.shinyapps.io/myshinyapp/](https://lmayhew.shinyapps.io/myshinyapp/)

## The Plot

```{r plot, echo=FALSE,message=FALSE}
library(DAAG)
dataX <- hurricNamed$LF.WindsMPH
dataY <- hurricNamed$BaseDamage

plot(dataX,dataY, 
               xlab="Windspeed (mph)", 
               ylab="Damage (Millions of US Dollars)",
               main="Damage from Named US Hurricanes",
               cex=1.5, pch=16, bty="n")
```

## The Model

The linear model used was from the function "lm".  The function being fit was

damage = m * windspeed + b

where m is the slope and b is the intercept.  In MyShinyApp you can take a 
subset of the data by selecting less than all of it and also by decreasing
the data range with a slider. Here, we use all the data to determine the coefficients.

```{r model, echo = TRUE, message=FALSE}
library(DAAG)
fit <- lm(BaseDamage~LF.WindsMPH, data=hurricNamed)
fit$coefficients
```

## Model and Plot

```{r modelAndPlot, echo=FALSE,message=FALSE}
plot(dataX,dataY, 
               xlab="Windspeed (mph)", 
               ylab="Damage (Millions of US Dollars)",
               main="Damage from Named US Hurricanes",
               cex=1.5, pch=16, bty="n")
abline(fit, col="blue",lwd=2)
```


